\bf Title

### 2024-03-11 article/paper_padic_spec.tex
commit by Simone

{\bf normalement avec la nouvelle definition, ça devrait aller, peut être il faudrait
  diviser la proposition en plusieures parties pour la rendre plus lisible}.

\begin{proposition}
Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
be a linear mapping. Then $f(\PP)$ is a polyhedron.
\end{proposition}
\begin{proof}
Let us assume that 
$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.

@@

Now, we turn our attention to the $\Delta$ part of $f.$
We first assume that $f$ is a projection 
of the form $K^n \rightarrow K^{n+1},$
$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$

@@

We present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in Smith normal form.
The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$. Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$. The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$. Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$ $Mz \geq 0$ if and only if $Sz \geq 0$.

That property applied to the matrix $A$ in \ref{LP} allow to reduce the problem to an equivalent simpler iteration of the \ref{LP} problem that will be called \emph{diagonal linear programming problem} \corentin{or maybe reduced linear programming problem?}. This problem is the optimization problem: \simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
\begin{equation}
  \tag{DLP}\label{DLP}
\begin{array}{rcll}
  p^* & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = s_1 \oplus s_2 \oplus \ldots \oplus s_r \oplus { \bm 0}_{m-r} $ for $r={\rm rank} S$.

@@

A vector $x^* \in K^n$ is \emph{feasible solution} of \ref{LP} if $Ax^* + b \geq 0$. Similarly, a vector $y^* \in K^n$ is a feasible of \ref{DLP} if $Sy^*+b' \geq 0$. We will denote as $Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.

\begin{proposition} 
  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL(\OK)$ such that $A=Q^{-1}SP$.
  We define $b':= Qb$ and $c':= (P^{-1})^Tc$. 
   \begin{enumerate}
    \item $x^* \in K^n$ is a feasible solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y^* = P x^*$ is a feasible solution of the \ref{DLP} problem of parameters $S, b'$ ans $c'$.
		\item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.
   \end{enumerate}
\end{proposition}
\begin{proof}
  First of all, 1. is a direct consequence of the fact that $Ax^*+b = AP^{-1}y^* +b\geq 0$ if and only if $Q(AP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.

>>>>

{\color{blue} Normalement avec la nouvelle definition, ça devrait aller, il faut par contre
  partir d'un polyedre defini aussi par des égalités. Peut être il faudrait aussi
  diviser la proposition en plusieures parties pour la rendre plus lisible, par exemple une
  première proposition avec la projection.}

\begin{proposition}
Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
be a linear mapping. Then $f(\PP)$ is a polyhedron.
\end{proposition}
\begin{proof}
Let us assume that 
$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.
{\color{blue} mettre aussi les égalités dans $\PP$}.

@@

Now, we turn our attention to the $\Delta$ part of $f.$
We first assume that $f$ is a projection 
of the form $K^n \rightarrow K^{n-1},$
$(x_1,\dots,x_{n-1},x_n)\mapsto (x_1,\dots,x_{n-1}).$

@@

We present an algorithm for solving \eqref{LP} which consists in reducing the matrix $A$ in Smith normal form.
The most interesting aspect in the SNF regarding the resolution of \ref{LP} is that the transition matrices are invertible in $\OK$. Indeed, if $z \in K^n$ and $M \in \allmat_n(\OK)$ such that $z \geq 0$ then $Mz \geq 0$. The latter property is a direct consequence of $\OK$ being a ring and the converse holds if the matrix $M$ is invertible in $\OK$. Therefore, for all matrix $M \in \allmat_n(K)$ with SNF $S$ and all $z \in K^n$, then $Mz \geq 0$ if and only if $Sz \geq 0$.

That property applied to the matrix $A$ in \ref{LP} allows to reduce the problem to an equivalent simpler iteration of the problem in \eqref{LP}, that will be called \emph{diagonal linear programming problem}
%%%\corentin{or maybe reduced linear programming problem?}:
%%%\simone{il me semble que tout ça n'est pas trop clair, par exemple quelle est la difference entre diagonal LP et associated diagonal LP plus en bas, est-ce qu'il y a vraiment besoin de tout ça, il faut simplifier la presentation}
\begin{equation}
  \tag{dLP}\label{DLP}
\begin{array}{rcll}
  {p^*}' & := & \inf_{y \in K^n} & \val(\left\langle c', y \right\rangle) \\
  &    & \text{s.t.}         & S y + b' \geq 0
\end{array}
\end{equation}
with $c' \in K^n$ a fixed vector of size $n$, $b' \in K^m$ and $S$ a diagonal $m \times n$ matrix of the form $S = \diag(s_1, s_2, \ldots, s_r, { \bm 0}_{m-r})$, with $r = {\rm rank}\, S$.

@@

A vector $x \in K^n$ is \emph{feasible} for \eqref{LP} if $Ax + b \geq 0$. Similarly, a vector $y \in K^n$ is feasible for \eqref{DLP} if $Sy+b' \geq 0$. We denote the \emph{feasible set} of \eqref{LP} and \eqref{DLP} respectively by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0\} \\
  \PP' &= \{y \in K^n : Sy + b' \geq 0\}.
\end{aligned}
\end{equation*}
A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \left\langle c,x^*\right\rangle$
(similarly for \eqref{DLP}).
%%%$Adm$ \corentin{Probablement à changer mais je ne sais pas quel nom lui donner} the set of feasible solution of \ref{DLP}.

\begin{proposition} 
  Let $A \in \allmat_{m,n}(K), b \in K^m, c\in K^n$ and let $S \in \allmat_{m,n}(K)$ be the Smith normal form of $A$ with transition matrices $P \in \GL_n(\OK)$ and $Q\in \GL_m(\OK)$ such that $A=Q^{-1}SP$.
  We define $b':= Qb$ and $c':= (P^{-1})^Tc$.  Then
   \begin{enumerate}
    \item $x^* \in K^n$ is feasible for \eqref{LP} if and only if $y^* = P x^* \in K^n$ is feasible for \eqref{DLP}.
    \item $x \in K^n$ is a solution of the \ref{LP} problem of parameters $A, b$ and $c$ if and only if $y = P x$ is a solution of the \ref{DLP} problem of parameters $S,b'$ and $c'$ and $\langle c,x \rangle = \langle c',y \rangle$.
   \end{enumerate}
\end{proposition}
\begin{proof}
  First of all, 1. is a direct consequence of the fact that $Ax^*+b = AP^{-1}y^* +b\geq 0$ if and only if $Q(AP^{-1}y^* + b) = Sy^* + b' \geq 0$ because $Q \in GL_m(\OK)$.
